Template for manuscript

### 2024-12-12 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Writing README files

fig2 <- ggarrange(p1 + rremove("xlab"), p2 + rremove("xlab"), p3 + rremove("xlab"),
                  p4 + rremove("xlab"), p5 + rremove("xlab"), p6 + rremove("xlab"),
                  p7 + rremove("xlab"), p8 + rremove("xlab"), nrow=4, ncol = 2,
                  common.legend = TRUE, legend = "bottom",
                  labels = c("A", "B", "C", "D", "E", "F", "G", "H"),label.x = -0.045,
                  align = "hv")

fig2 <- annotate_figure(fig2) +
  theme(plot.margin = margin(t = 5, r = 12, b = 5, l = 12))
print(fig2)
@
\vspace{0.5cm}

>>>>

fig2 <- ggarrange(p1 + rremove("xlab"), p2 + rremove("xlab"), p3 + rremove("xlab"),
                  p4 + rremove("xlab"), p5 + rremove("xlab"), p6 + rremove("xlab"),
                  p7 + rremove("xlab"), p8 + rremove("xlab"), nrow=4, ncol = 2,
                  common.legend = TRUE, legend = "top",
                  labels = c("A", "B", "C", "D", "E", "F", "G", "H"),label.x = -0.043,
                  align = "hv")

fig2 <- annotate_figure(fig2) +
  theme(plot.margin = margin(t = 5, r = 8, b = 5, l = 12))
print(fig2)
@
\vspace{0.5cm}
